test_imputed

### 2016-05-26 rf_log_naiive_auc.rmd
backwards at work

```{r, echo=FALSE}
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library('ggplot2',lib='C:/Progra~1/R/R-3.2.1/library')
library('gbm', lib = 'C:/Progra~1/R/R-3.2.2/library')
library('caret', lib = 'C:/Progra~1/R/R-3.2.2/library')
library('pROC',lib='C:/Progra~1/R/R-3.2.2/library')
library('e1071',lib='C:/Progra~1/R/R-3.2.2/library')
library('randomForest',lib='C:/Progra~1/R/R-3.2.2/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')

@@

>>>>

```{r, echo=FALSE}
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library('ggplot2')
library('gbm')
library('caret')
library('pROC')
library('e1071')
library('randomForest')
library('party')

@@

Checking p value for BN

```{r}
reduc.totAUC <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/reduc_df_auc.rds")
BN = read.csv("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/BN_AUCs.csv")

n.samples(data = list(reduc.totAUC[[2]][1:20], BN$AUC), type.calc = 'two.sample', alt = 'two.sided')

# only 5 samples required according to power calculation
